\chapter{Usage}\label{ch:usage}

This chapter explains all the settings that are necessary for the project to run. More specifically, it shows the \textit{Maven} \textit{POM} file and the properties file needed to set up the environment correctly. The project on \href{\projRoot}{Github} also contains a bash script with an example of how the program can be run.

\section{Project Object Model}\label{sec:pom}

The POM contains information about the project and various configuration details used by Maven to build the project.

In order to compile the instrumented class under test, a specific \emph{JDK} library has to be imported as a dependency inside the project. 
%This compiler lib is necessary for the under test class to be available and executable at run-time after the code instrumentation.

Since this library depends on the \emph{JDK} and therefore on the machine architecture, a \emph{<profile>} tag is necessary to specify the path to this library for different operating systems, in order to maintain the code machine independent.

\begin{lstlisting}[language=XML,caption={Windows default profile for jdk lib},label={lst:winToolsJar}]% Start your code-block

<profile>
	<id>windows_profile</id>
	<activation>
		<os>
			<family>Windows</family>
		</os>
	</activation>
	<properties>
		<toolsjar>${java.home}\..\lib\tools.jar</toolsjar>
	</properties>
</profile>
\end{lstlisting}

Indeed, there are specific paths for each OS type, and Maven accepts only specific \href{http://maven.apache.org/enforcer/enforcer-rules/requireOS.html}{\textit{OS families}}.

The tag \textit{<toolsjar>} is an ad-hoc tag created to define a new property, in this case the path to the tools.jar library. In \autoref{lst:instToolsJar}, there are a few elements to consider. First, the maven \textit{phase} in which the installation of this library has to be performed that is, in this case, the \textit{install} phase. Second, the \textit{configuration} of tools.jar is based on the JDK installed on the system. The  plugin tag in \autoref{lst:instToolsJar} is necessary to install libraries in the maven local repository, in this case the one defined with the profile above (\autoref{lst:winToolsJar}). Differently from above, this part does not require a cross-platform extension, because the elements in the configuration tag are the same for all operating systems. However, the version depends on the JDK installed, so it has to be updated accordingly.

\begin{lstlisting}[language=XML,caption={How to 'mvn install' the tools.jar},label={lst:instToolsJar}]% Start your code-block

<plugin>
	<groupId>org.apache.maven.plugins</groupId>
	<artifactId>maven-install-plugin</artifactId>
	<version>2.5.2</version>
	<executions>
		<execution>
			<id>install-external</id>
			<phase>install</phase>
			<configuration>
				<file>${toolsjar}</file>
				<repositoryLayout>default</repositoryLayout>
				<groupId>com.sun</groupId>
				<artifactId>tools</artifactId>
				<version>1.8.0</version>
				<packaging>jar</packaging>
				<generatePom>true</generatePom>
			</configuration>
			<goals>
				<goal>install-file</goal>
			</goals>
		</execution>
	</executions>
</plugin>
\end{lstlisting}

\section{Properties}\label{sec:prop}
A .properties is a file extension for files used in Java programs to specify the configurable parameters of a Java application. WRGen requires information about the specific class under test that has to analyze. More specifically, a list of all the properties that are configurable in WRGen is shown below:

\begin{itemize}
	\item \textbf{FileName}: the \textit{complete} name (package names included) of the class under test, is required.	E.g.: FileName = com.main.ClassUnderTest;
	\item \textbf{ProjectName}: the name of the java project that contains the class under test is required;
	\item \textbf{PathToProjectDir}: the absolute path of the java project that contains the class under test;
	\item \textbf{LineToCover}: colon separated list of numbers representing the lines to cover in the class under test. E.g.:LineToCover = 33:47:60:72:85:99:115:132:144:157
	\item \textbf{Separator}: in the LineToCover property the default separator is the colon, but a different one can be used which can be specified in this property;
	\item \textbf{ExecutionTestTimer}: timeout in milliseconds for the test generation phase of WRGen;
	\item \textbf{MaxNumberOfMethodXTest}: each test case has a random length. In this property the user specifies the maximum length of a test case;
	\item \textbf{GraphName}: name of the web application graph ;
	\item \textbf{GraphDirPath}: absolute path of the dot file containing the web application graph;
	\item \textbf{StartNodeGraph}: name of the node in the web application graph modelling the home page of the web application under test;
	\item \textbf{RequiredPath}: The program uses reflection to execute the class under test. Hence, here it is required the classpath of the Java project containing the class under test.
\end{itemize}